---
author: "KSejas"
date: "`r format(Sys.Date(), '%b %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(caret)
library(tidyverse)
library(viridis)
library(MASS)
library(dplyr) 

library(broom)
library(tidymodels)
library(glmnet)
library(data.table)
library(e1071)
library(kernlab)
```



Training Data

```{r}
haiti_train <- read.csv("/Users/k/Downloads/DS6030/Project/HaitiPixels.csv", header=TRUE)

haiti_train<-haiti_train %>%  
  mutate(flag_blue_tarp = case_when(Class=="Blue Tarp" ~ "Blue_Tarp",  
                                 Class!="Blue Tarp" ~ "Not_Blue_Tarp")) 
haiti_train<-haiti_train %>%  
  mutate(flag_blue_tarp_label = case_when(Class=="Blue Tarp" ~ "Blue Tarp",  
                                 Class!="Blue Tarp" ~ "Not Blue Tarp")) # plots 

haiti_train$flag_blue_tarp<-factor(haiti_train$flag_blue_tarp, levels=c("Blue_Tarp", "Not_Blue_Tarp")) 
levels(haiti_train$flag_blue_tarp) 

haiti_train$flag_blue_tarp_label<-factor(haiti_train$flag_blue_tarp_label, levels=c("Blue Tarp", "Not Blue Tarp")) 
```


Holdout Data 

```{r}
h1 <- read_table("/Users/k/Downloads/DS6030/Project/Hold Out Data/orthovnir057_ROI_NON_Blue_Tarps.txt", skip=8, col_names=FALSE, col_types=cols(
  X1 = col_double(),
  X2 = col_double(),
  X3 = col_double(),
  X4 = col_double(),
  X5 = col_double(),
  X6 = col_double(),
  X7 = col_double(),
  X8 = col_double(),
  X9 = col_double(),
  X10 = col_double()
))
h1 <- h1[,-1]
colnames(h1) <- c("x", "y", "map_x", "map_y", "lat", "lon", "b1", "b2", "b3")
h1["source_type"]<- "NON_BLUE_TARPS"
h1["source"]<- "orthovnir057_ROI_NON_Blue_Tarps"
```


This file is not needed. 
```{r}
h2 <- read_table("/Users/k/Downloads/DS6030/Project/Hold Out Data/orthovnir067_ROI_Blue_Tarps_data.txt", skip=1, col_names=FALSE, col_types=cols(
   X1 = col_double(),
   X2 = col_double(),
   X3 = col_double()
))
colnames(h2) <- c("b1", "b2", "b3")

```



```{r}
h3 <- read_table("/Users/k/Downloads/DS6030/Project/Hold Out Data/orthovnir067_ROI_Blue_Tarps.txt", skip=8, col_names=FALSE, col_types=cols(
  X1 = col_double(),
  X2 = col_double(),
  X3 = col_double(),
  X4 = col_double(),
  X5 = col_double(),
  X6 = col_double(),
  X7 = col_double(),
  X8 = col_double(),
  X9 = col_double(),
  X10 = col_double()
))
h3 <- h3[,-1]
colnames(h3) <- c("x", "y", "map_x", "map_y", "lat", "lon", "b1", "b2", "b3")

h3["source_type"]<- "BLUE_TARPS"
h3["source"]<- "orthovnir067_ROI_Blue_Tarps"
```



```{r}
h4 <- read_table("/Users/k/Downloads/DS6030/Project/Hold Out Data/orthovnir067_ROI_NOT_Blue_Tarps.txt", skip=8, col_names=FALSE, col_types=cols(
  X1 = col_double(),
  X2 = col_double(),
  X3 = col_double(),
  X4 = col_double(),
  X5 = col_double(),
  X6 = col_double(),
  X7 = col_double(),
  X8 = col_double(),
  X9 = col_double(),
  X10 = col_double()
))
h4 <- h4[,-1]
colnames(h4) <- c("x", "y", "map_x", "map_y", "lat", "lon", "b1", "b2", "b3")

h4["source_type"]<- "NOT_BLUE_TARPS"
h4["source"]<- "orthovnir067_ROI_NOT_Blue_Tarps"
```


```{r}
h5 <- read_table("/Users/k/Downloads/DS6030/Project/Hold Out Data/orthovnir069_ROI_Blue_Tarps.txt", skip=8, col_names=FALSE, col_types=cols(
  X1 = col_double(),
  X2 = col_double(),
  X3 = col_double(),
  X4 = col_double(),
  X5 = col_double(),
  X6 = col_double(),
  X7 = col_double(),
  X8 = col_double(),
  X9 = col_double(),
  X10 = col_double()
))
h5 <- h5[,-1]
colnames(h5) <- c("x", "y", "map_x", "map_y", "lat", "lon", "b1", "b2", "b3")

h5["source_type"]<- "BLUE_TARPS"
h5["source"]<- "orthovnir069_ROI_Blue_Tarps"
```


```{r}
h6 <- read_table("/Users/k/Downloads/DS6030/Project/Hold Out Data/orthovnir069_ROI_NOT_Blue_Tarps.txt", skip=8, col_names=FALSE, col_types=cols(
  X1 = col_double(),
  X2 = col_double(),
  X3 = col_double(),
  X4 = col_double(),
  X5 = col_double(),
  X6 = col_double(),
  X7 = col_double(),
  X8 = col_double(),
  X9 = col_double(),
  X10 = col_double()
))
h6 <- h6[,-1]
colnames(h6) <- c("x", "y", "map_x", "map_y", "lat", "lon", "b1", "b2", "b3")

h6["source_type"]<- "NOT_BLUE_TARPS"
h6["source"]<- "orthovnir069_ROI_NOT_Blue_Tarps"
```



```{r}
h7 <- read_table("/Users/k/Downloads/DS6030/Project/Hold Out Data/orthovnir078_ROI_Blue_Tarps.txt", skip=8, col_names=FALSE, col_types=cols(
  X1 = col_double(),
  X2 = col_double(),
  X3 = col_double(),
  X4 = col_double(),
  X5 = col_double(),
  X6 = col_double(),
  X7 = col_double(),
  X8 = col_double(),
  X9 = col_double(),
  X10 = col_double()
))
h7 <- h7[,-1]
colnames(h7) <- c("x", "y", "map_x", "map_y", "lat", "lon", "b1", "b2", "b3")
h7["source_type"]<- "BLUE_TARPS"
h7["source"]<- "orthovnir078_ROI_Blue_Tarps"
```



```{r}
h8 <- read_table("/Users/k/Downloads/DS6030/Project/Hold Out Data/orthovnir078_ROI_NON_Blue_Tarps.txt", skip=8, col_names=FALSE, col_types=cols(
  X1 = col_double(),
  X2 = col_double(),
  X3 = col_double(),
  X4 = col_double(),
  X5 = col_double(),
  X6 = col_double(),
  X7 = col_double(),
  X8 = col_double(),
  X9 = col_double(),
  X10 = col_double()
))
h8 <- h8[,-1]
colnames(h8) <- c("x", "y", "map_x", "map_y", "lat", "lon", "b1", "b2", "b3")
h8["source_type"]<- "NON_BLUE_TARPS"
h8["source"]<- "orthovnir078_ROI_NON_Blue_Tarps"
```

```{r}
df_list <-list(h1, h3, h4, h5, h6, h7, h8)
haiti<- rbindlist(df_list, use.names=TRUE, fill=FALSE, idcol=NULL)

rownames(haiti)<- 1:nrow(haiti)
```

```{r}
haiti<-haiti %>% 
  mutate(flag_blue_tarp = case_when(source_type=="BLUE_TARPS" ~ "Blue_Tarp", 
                                 source_type!="BLUE_TARPS" ~ "Not_Blue_Tarp"))

haiti<-haiti %>% 
  mutate(class = case_when(source_type=="BLUE_TARPS" ~ "Blue Tarp", 
                                 source_type!="BLUE_TARPS" ~ "Not Blue Tarp")) # plots

haiti$flag_blue_tarp<-factor(haiti$flag_blue_tarp, levels=c("Blue_Tarp", "Not_Blue_Tarp"))
levels(haiti$flag_blue_tarp)

haiti$class<-factor(haiti$class, levels=c("Blue Tarp", "Not Blue Tarp"))

```

Sample of Stacked Holdout Dataset used for EDA Scatterplot Graphs 

```{r}
  set.seed(1)  
  split=0.4 
  index <- caret::createDataPartition(haiti[,flag_blue_tarp], p=split, list=FALSE)
  samp <- haiti[index, ]
```


# Exploratory Data Analysis


```{r}
plot_f<- function(d, t){
  ggplot(d, aes(class))+
  geom_bar(fill = "#0073C2FF")+
  ggtitle(t)+
  xlab("Class")+ 
  ylab("Count")+ 
  theme(plot.title = element_text(size=12), axis.text.x=element_text(size=11))
}
plot_f(haiti, "Class Frequency")
```

```{r}
haiti_bluetarp <- haiti[which(haiti$flag_blue_tarp == "Blue_Tarp"),]
```

```{r}
haiti_bluetarp_t <- haiti_train[which(haiti_train$Class == "Blue Tarp"),]
```

```{r}
plot_f<- function(v, v_t, title){  
ggplot(haiti_train, aes(x=flag_blue_tarp_label, y=v))+  
  geom_boxplot()+  
  labs(x="Whether Blue Tarp", y=v_t, title=title)  
}  
plot_f(haiti_train$Red, "Red", "Distribution of Red Pixels by Blue Tarp Identification")  
plot_f(haiti_train$Green, "Green", "Distribution of Green Pixels by Blue Tarp Identification")  
plot_f(haiti_train$Blue, "Blue", "Distribution of Blue Pixels by Blue Tarp Identification") 
```



```{r}
plot_f<- function(v, v_t, title){
ggplot(haiti, aes(x=class, y=v))+
  geom_boxplot()+
  labs(x="Whether Blue Tarp", y=v_t, title=title)
}
plot_f(haiti$b1, "B1", "Distribution of B1 Pixels by Blue Tarp Identification using Stacked Holdout Dataset")
plot_f(haiti$b2, "B2", "Distribution of B2 Pixels by Blue Tarp Identification using Stacked Holdout Dataset")
plot_f(haiti$b3, "B3", "Distribution of B3 Pixels by Blue Tarp Identification using Stacked Holdout Dataset")
```

```{r}
ggplot(haiti_train, aes(x=Red, y=Blue, color=Class))+
  geom_point(alpha=0.2)+
  labs(x='Red', y='Blue', title='Scatterplot of Blue Pixels Against Red Pixels')+
  scale_color_manual(values=c("royalblue1", "gray52", "tan4", "magenta1", "green4"))

```
```{r}
haiti_bluetarp_t2 <- haiti_bluetarp_t[which(haiti_bluetarp_t$Blue == 255),]
```

```{r}
ggplot(haiti_train, aes(x=Green, y=Blue, color=Class))+
  geom_point(alpha=0.2)+
  labs(x='Green', y='Blue', title='Scatterplot of Blue Pixels Against Green Pixels')+
  scale_color_manual(values=c("royalblue1", "gray52", "tan4", "magenta1", "green4"))

```



```{r}

ggplot(samp, aes(x=b1, y=b3, color=class))+
  geom_point(alpha=0.2)+
  labs(x='B1 (red)', y='B3 (blue)', title='Scatterplot of B3 (Blue) Pixels Against B1 (Red) Pixels')+
  scale_color_manual(values=c("royalblue1", "gray52"))

```

```{r}
haiti_bluetarp2 <- haiti_bluetarp[which(haiti_bluetarp$b3 == 255),]
```

```{r}

ggplot(samp, aes(x=b2, y=b3, color=class))+
  geom_point(alpha=0.2)+
  labs(x='B2 (green)', y='B3 (blue)', title='Scatterplot of B3 (Blue) Pixels Against B2 (Green) Pixels')+
  scale_color_manual(values=c("royalblue1", "gray52"))

```
# Tuning Process 

# KNN Tuning Process


```{r}
  set.seed(1)  
  folds <- createFolds(haiti_train$flag_blue_tarp, k = 10, list = TRUE, returnTrain = TRUE)
  kvals<- data.frame(k=seq(1, 100, by=2))
  kfolds <- 10
  Control <- caret::trainControl(method='cv', number=kfolds, index = folds, savePredictions = "final", classProbs = TRUE)
  
  model <- caret::train(flag_blue_tarp ~ Blue + Green + Red, data=haiti_train,
               method='knn',  
               tuneGrid=kvals,
               metric = 'Accuracy',
               trControl=Control
               )  

  model$results %>% slice_max(Accuracy)
```
```{r}
model_results <- model$results
model_results$Error_Rate <- (1-model_results$Accuracy)*100

ggplot(model_results, aes(x=k, y=Error_Rate)) +
  geom_point() +
  geom_line() +
  labs(x="k", y="Error Rate (%)", title="Error Rate by K Value")
```
  
  
```{r}

  kvals<- data.frame(k=seq(1, 5, by=1))
  kfolds <- 10
  Control <- caret::trainControl(method='cv', number=kfolds, index = folds, savePredictions = "final", classProbs = TRUE)
  
  model_2 <- caret::train(flag_blue_tarp ~ Blue + Green + Red, data=haiti_train,
               method='knn',  
               tuneGrid=kvals,
               metric = 'Accuracy',
               trControl=Control
               )  

  model_2$results %>% slice_max(Accuracy)
```


```{r}
model_results_2 <- model_2$results
model_results_2$Error_Rate <- (1-model_results_2$Accuracy)*100

ggplot(model_results_2, aes(x=k, y=Error_Rate)) +
  geom_point() +
  geom_line() +
  labs(x="k", y="Error Rate (%)", title="Error Rate by K Value")
```
  
  

# Penalized Logistic Regression Tuning Process



```{r}

fmla = as.formula(flag_blue_tarp ~ Blue + Green + Red)  
#-- Logistic Regression (unpenalized)
fit.logistic = glm(fmla, family=binomial(), data=haiti_train)
tidy(fit.logistic) %>% head()

```

```{r}
#-- Option 1: using model.matrix()
X.train = model.matrix(fmla, data = haiti_train)[,-1] # remove intercept term
Y.train = haiti_train$flag_blue_tarp
```

```{r}
fit.ridge = glmnet(X.train, Y.train,
                   alpha = 0,          # this uses ridge penalty
                   family="binomial")  
opar=par(mfrow=c(1,2))
plot(fit.ridge, "norm")   
plot(fit.ridge, "lambda")   
```


```{r}
par(opar)
tidy(fit.ridge) %>% head()   # coefficients for set of lambda values
```




```{r}
set.seed(1)
e_net_p = cv.glmnet(x = X.train, y=Y.train, alpha=0.5,
                     family="binomial")

(lambda.hat = e_net_p$lambda.min)

coef(e_net_p, s="lambda.min")
plot(e_net_p)
```
# Support Vector Machine Tuning 

Linear Kernel: 


```{r}
set.seed(1)
tune_svm <- tune(svm, flag_blue_tarp ~ Blue + Green + Red, data = haiti_train, kernel = "linear", 
    ranges = list(cost = c(0.001, 0.01, 0.1, 1, 5, 10, 100, 125, 130, 135, 140, 145, 150, 175, 200)))
```

```{r}
summary(tune_svm)
```



```{r}
bestmod <- tune_svm$best.model
summary(bestmod)
```


Radial Kernel: 


```{r}
  set.seed(1)  
  split=0.4 
  index <- caret::createDataPartition(haiti_train[,'flag_blue_tarp'], p=split, list=FALSE)
  samp_svm <- haiti_train[index, ]
  
```


```{r}
set.seed(1)
fit_radial <- tune(svm, flag_blue_tarp ~ Blue + Green + Red, data = samp_svm, kernel = "radial",  
    ranges = list(cost = c(0.001, 0.01, 0.1, 1, 5, 10, 100, 125, 130, 135, 140, 145, 150, 175, 200), gamma = c(0.001, 0.01, 0.1, 1, 5, 10, 25, 50, 75, 100)))
```

```{r}
summary(fit_radial)
```






```{r}
bestmod <- fit_radial$best.model
summary(bestmod)
```



Polynomial Kernel Tuning: 

```{r}
set.seed(1)
fit_poly <- tune(svm, flag_blue_tarp ~ Blue + Green + Red, data = samp_svm, kernel = "polynomial",  
    ranges = list(cost = c(0.001, 0.01, 0.1, 1, 5, 10, 100, 125, 130, 135, 140, 145, 150, 175, 200), degree = c(2, 3, 4, 5, 6, 7)))
```

```{r}
summary(fit_poly)
```






```{r}
bestmod <- fit_poly$best.model
summary(bestmod)
```




# Model Training  

```{r}
  set.seed(1)  
  kfolds <- 10
  folds <- createFolds(haiti_train$flag_blue_tarp, k = 10, list = TRUE, returnTrain = TRUE)
  Control <- caret::trainControl(method='cv', number=kfolds, index = folds, savePredictions = "final", classProbs = TRUE)
  
  model_glm <- caret::train(flag_blue_tarp ~ Blue + Green + Red, data=haiti_train,
                        method='glm',  
                        tuneGrid=NULL,
                        trControl=Control,
                        family='binomial')  

  model_lda <- caret::train(flag_blue_tarp ~ Blue + Green + Red, data=haiti_train,
                        method='lda',  
                        tuneGrid=NULL,
                        trControl=Control
                        )  
  
  model_qda <- caret::train(flag_blue_tarp ~ Blue + Green + Red, data=haiti_train,
                        method='qda',  
                        tuneGrid=NULL,
                        trControl=Control
                        )  
  
  model_knn <- caret::train(flag_blue_tarp ~ Blue + Green + Red, data=haiti_train,
                        method='knn',  
                        tuneGrid=expand.grid(k=3),
                        trControl=Control
               )  
  
  model_plr <- caret::train(flag_blue_tarp ~ Blue + Green + Red, data=haiti_train,
                        method='plr',  
                        tuneGrid=expand.grid(lambda=0, cp="bic"),
                        trControl=Control
                        )  
  
  model_rf <- caret::train(flag_blue_tarp ~ Blue + Green + Red, data=haiti_train,
                        method='rf',  
                        tuneGrid=expand.grid(mtry=2),
                        trControl=Control,
                        ntree=500
                        )  
  
  model_svm_l <- caret::train(flag_blue_tarp ~ Blue + Green + Red, data=haiti_train,
                        method='svmLinear',  
                        tuneGrid=data.frame(C=135),
                        trControl=Control
                        )  
```

```{r}
  model_svm_r <- caret::train(flag_blue_tarp ~ Blue + Green + Red, data=haiti_train,
                        method='svmRadial',  
                        tuneGrid=expand.grid(C=10, sigma=25),
                        trControl=Control
                        )  
```



```{r}

haiti <- haiti %>%
    rename(Blue = b3,
           Green = b2, 
           Red = b1)

evaluateModel <- function(method, tuneGrid, outcome, title_m, model_sel, ...) {

  preds <- predict(model_sel, haiti)

  metrics <- caret::postResample(pred = preds, obs = haiti[, flag_blue_tarp])

  pred_r <- predict(model_sel, haiti, type='prob')
  pred_r_ob <- ROCR::prediction(pred_r$Not_Blue_Tarp, haiti$flag_blue_tarp, label.ordering=c('Blue_Tarp', 'Not_Blue_Tarp'))
  model.roc <- ROCR::performance(pred_r_ob, measure='tpr', x.measure='fpr')
  plot(model.roc, colorize=T, print.cutoffs.at=c(0, 0.1, 0.9, 1.0))
  lines(x=c(0,1), y=c(0,1), col='grey')
  title(main=title_m)
  
  ROCR::performance(pred_r_ob,"auc")@y.values[[1]]
  
  return( tibble(
    Method = method, 
    Accuracy = metrics['Accuracy'],
    ErrorRate = 1 - metrics['Accuracy'],
    AUC = ROCR::performance(pred_r_ob,"auc")@y.values[[1]]
  ))
    
}

results <- rbind(
  evaluateModel('glm', NULL, 'flag_blue_tarp', "Logistic Regression ROC Curve", model_glm),
  evaluateModel('lda', NULL, 'flag_blue_tarp', "LDA ROC Curve", model_lda),
  evaluateModel('qda', NULL, 'flag_blue_tarp', "QDA ROC Curve", model_qda),
  evaluateModel('knn', expand.grid(k=3), 'flag_blue_tarp', "KNN ROC Curve", model_knn),
  evaluateModel('plr', expand.grid(lambda=0, cp="bic"), 'flag_blue_tarp', "Penalized Logistic Regression ROC Curve", model_plr),
  evaluateModel('rf', expand.grid(mtry=2), 'flag_blue_tarp', "Random Forest ROC Curve", model_rf),
  evaluateModel('svmLinear', data.frame(C=135), 'flag_blue_tarp', "Support Vector Machine Linear Kernel ROC Curve", model_svm_l),
  evaluateModel('svmRadial', expand.grid(C=10, sigma=25), 'flag_blue_tarp', "Support Vector Machine Radial Kernel ROC Curve", model_svm_r)
)  
bestModels <- which.max(results$Accuracy)
results %>% 
  knitr::kable(digits=3)  %>%
  kableExtra::kable_styling(full_width=FALSE)  %>%
  kableExtra::row_spec(bestModels, bold=TRUE, background='#D3D3D3')
```

# Selecting a Threshold Value


# Logistic Regression Threshold Value Selection

  All probability thresholds table: 


```{r}

  threshold.stats <- caret::thresholder(model_glm,
                                        threshold = seq(0.05, 0.95, by = 0.05),
                                        statistics = "all")
  threshold.stats$TPR <- threshold.stats$Sensitivity
  threshold.stats$TNR <- threshold.stats$Specificity
  
  
  threshold.stats$FNR <- 1 - threshold.stats$Sensitivity
  threshold.stats$FPR <- 1 - threshold.stats$Specificity
  
  threshold.stats %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE)
```



  Smallest False Negative Rate 
```{r}
  threshold.stats %>% slice_min(FNR) %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE)
```



  Smallest False Positive Rate

```{r}
  threshold.stats %>% slice_min(FPR) %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE)  
```



 Smallest distance to top left in the ROC curve

```{r}
  threshold.stats %>% slice_min(Dist) %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE) 
```

```{r}
  minDistance <- threshold.stats %>% slice_min(Dist)
  ggplot(threshold.stats, aes(x=prob_threshold, y=Dist)) +
    geom_line() +
    geom_point(data=minDistance, color="red")+
    xlab("Probability Threshold")+
    ylab("Distance to Top Left in the ROC Curve")+
    ggtitle("Distance to Top Left in the ROC Curve by Probability Threshold")
    
```




# LDA Threshold Value Selection

  All probability thresholds table: 

```{r}

  threshold.stats <- caret::thresholder(model_lda,
                                        threshold = seq(0.05, 0.95, by = 0.05),
                                        statistics = "all")
  threshold.stats$TPR <- threshold.stats$Sensitivity
  threshold.stats$TNR <- threshold.stats$Specificity
  
  
  threshold.stats$FNR <- 1 - threshold.stats$Sensitivity
  threshold.stats$FPR <- 1 - threshold.stats$Specificity
  
  threshold.stats %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE)
```



  Smallest False Negative Rate 
```{r}
  threshold.stats %>% slice_min(FNR) %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE)
```



  Smallest False Positive Rate

```{r}
  threshold.stats %>% slice_min(FPR) %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE)  
```



 Smallest distance to top left in the ROC curve

```{r}
  threshold.stats %>% slice_min(Dist) %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE) 
```


```{r}
  minDistance <- threshold.stats %>% slice_min(Dist)
  ggplot(threshold.stats, aes(x=prob_threshold, y=Dist)) +
    geom_line() +
    geom_point(data=minDistance, color="red")+
    xlab("Probability Threshold")+
    ylab("Distance to Top Left in the ROC Curve")+
    ggtitle("Distance to Top Left in the ROC Curve by Probability Threshold")
    
```




# QDA Threshold Value Selection

  All probability thresholds table: 

```{r}
  
  threshold.stats <- caret::thresholder(model_qda,
                                        threshold = seq(0.05, 0.95, by = 0.05),
                                        statistics = "all")
  threshold.stats$TPR <- threshold.stats$Sensitivity
  threshold.stats$TNR <- threshold.stats$Specificity
  
  
  threshold.stats$FNR <- 1 - threshold.stats$Sensitivity
  threshold.stats$FPR <- 1 - threshold.stats$Specificity
  
  threshold.stats %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE)
```



  Smallest False Negative Rate 
```{r}
  threshold.stats %>% slice_min(FNR) %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE)
```



  Smallest False Positive Rate

```{r}
  threshold.stats %>% slice_min(FPR) %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE)  
```



 Smallest distance to top left in the ROC curve

```{r}
  threshold.stats %>% slice_min(Dist) %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE) 
```

```{r}
  minDistance <- threshold.stats %>% slice_min(Dist)
  ggplot(threshold.stats, aes(x=prob_threshold, y=Dist)) +
    geom_line() +
    geom_point(data=minDistance, color="red")+
    xlab("Probability Threshold")+
    ylab("Distance to Top Left in the ROC Curve")+
    ggtitle("Distance to Top Left in the ROC Curve by Probability Threshold")
    
```




# KNN Threshold Value Selection 

  All probability thresholds table: 

```{r}

  threshold.stats <- caret::thresholder(model_knn,
                                        threshold = seq(0.05, 0.95, by = 0.05),
                                        statistics = "all")
  threshold.stats$TPR <- threshold.stats$Sensitivity
  threshold.stats$TNR <- threshold.stats$Specificity
  
  
  threshold.stats$FNR <- 1 - threshold.stats$Sensitivity
  threshold.stats$FPR <- 1 - threshold.stats$Specificity
  
  threshold.stats %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE)
```



  Smallest False Negative Rate 
```{r}
  threshold.stats %>% slice_min(FNR) %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE)
```



  Smallest False Positive Rate

```{r}
  threshold.stats %>% slice_min(FPR) %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE)  
```



 Smallest distance to top left in the ROC curve

```{r}
  threshold.stats %>% slice_min(Dist) %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE) 
```

```{r}
  minDistance <- threshold.stats %>% slice_min(Dist)
  ggplot(threshold.stats, aes(x=prob_threshold, y=Dist)) +
    geom_line() +
    geom_point(data=minDistance, color="red")+
    xlab("Probability Threshold")+
    ylab("Distance to Top Left in the ROC Curve")+
    ggtitle("Distance to Top Left in the ROC Curve by Probability Threshold")
    
```



# Penalized Logistic Regression Threshold Value Selection 

  All probability thresholds table: 

```{r}

  threshold.stats <- caret::thresholder(model_plr,
                                        threshold = seq(0.05, 0.95, by = 0.05),
                                        statistics = "all")
  threshold.stats$TPR <- threshold.stats$Sensitivity
  threshold.stats$TNR <- threshold.stats$Specificity
  
  
  threshold.stats$FNR <- 1 - threshold.stats$Sensitivity
  threshold.stats$FPR <- 1 - threshold.stats$Specificity
  
  threshold.stats %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE)
```



  Smallest False Negative Rate 
```{r}
  threshold.stats %>% slice_min(FNR) %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE)
```



  Smallest False Positive Rate

```{r}
  threshold.stats %>% slice_min(FPR) %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE)  
```



 Smallest distance to top left in the ROC curve

```{r}
  threshold.stats %>% slice_min(Dist) %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE) 
```

```{r}
  minDistance <- threshold.stats %>% slice_min(Dist)
  ggplot(threshold.stats, aes(x=prob_threshold, y=Dist)) +
    geom_line() +
    geom_point(data=minDistance, color="red")+
    xlab("Probability Threshold")+
    ylab("Distance to Top Left in the ROC Curve")+
    ggtitle("Distance to Top Left in the ROC Curve by Probability Threshold")
    
```



# Random Forest Threshold Value Selection 

  All probability thresholds table: 

```{r}

  threshold.stats <- caret::thresholder(model_rf,
                                        threshold = seq(0.05, 0.95, by = 0.05),
                                        statistics = "all")
  threshold.stats$TPR <- threshold.stats$Sensitivity
  threshold.stats$TNR <- threshold.stats$Specificity
  
  
  threshold.stats$FNR <- 1 - threshold.stats$Sensitivity
  threshold.stats$FPR <- 1 - threshold.stats$Specificity
  
  threshold.stats %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE)
```



  Smallest False Negative Rate 
```{r}
  threshold.stats %>% slice_min(FNR) %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE)
```



  Smallest False Positive Rate

```{r}
  threshold.stats %>% slice_min(FPR) %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE)  
```



 Smallest distance to top left in the ROC curve

```{r}
  threshold.stats %>% slice_min(Dist) %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE) 
```

```{r}
  minDistance <- threshold.stats %>% slice_min(Dist)
  ggplot(threshold.stats, aes(x=prob_threshold, y=Dist)) +
    geom_line() +
    geom_point(data=minDistance, color="red")+
    xlab("Probability Threshold")+
    ylab("Distance to Top Left in the ROC Curve")+
    ggtitle("Distance to Top Left in the ROC Curve by Probability Threshold")
    
```



# Support Vector Machine Linear Kernel Threshold Value Selection 

  All probability thresholds table: 

```{r}

  threshold.stats <- caret::thresholder(model_svm_l,
                                        threshold = seq(0.05, 0.95, by = 0.05),
                                        statistics = "all")
  threshold.stats$TPR <- threshold.stats$Sensitivity
  threshold.stats$TNR <- threshold.stats$Specificity
  
  
  threshold.stats$FNR <- 1 - threshold.stats$Sensitivity
  threshold.stats$FPR <- 1 - threshold.stats$Specificity
  
  threshold.stats %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE)
```



  Smallest False Negative Rate 
```{r}
  threshold.stats %>% slice_min(FNR) %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE)
```



  Smallest False Positive Rate

```{r}
  threshold.stats %>% slice_min(FPR) %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE)  
```



 Smallest distance to top left in the ROC curve

```{r}
  threshold.stats %>% slice_min(Dist) %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE) 
```

```{r}
  minDistance <- threshold.stats %>% slice_min(Dist)
  ggplot(threshold.stats, aes(x=prob_threshold, y=Dist)) +
    geom_line() +
    geom_point(data=minDistance, color="red")+
    xlab("Probability Threshold")+
    ylab("Distance to Top Left in the ROC Curve")+
    ggtitle("Distance to Top Left in the ROC Curve by Probability Threshold")
    
```



# Support Vector Machine Radial Kernel Threshold Value Selection 

  All probability thresholds table: 

```{r}

  threshold.stats <- caret::thresholder(model_svm_r,
                                        threshold = seq(0.05, 0.95, by = 0.05),
                                        statistics = "all")
  threshold.stats$TPR <- threshold.stats$Sensitivity
  threshold.stats$TNR <- threshold.stats$Specificity
  
  
  threshold.stats$FNR <- 1 - threshold.stats$Sensitivity
  threshold.stats$FPR <- 1 - threshold.stats$Specificity
  
  threshold.stats %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE)
```



  Smallest False Negative Rate 
```{r}
  threshold.stats %>% slice_min(FNR) %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE)
```



  Smallest False Positive Rate

```{r}
  threshold.stats %>% slice_min(FPR) %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE)  
```



 Smallest distance to top left in the ROC curve

```{r}
  threshold.stats %>% slice_min(Dist) %>% 
    dplyr::select("prob_threshold", "Accuracy", "FNR", "FPR", "Dist", "F1", "TPR", "TNR", "Precision") %>%
    knitr::kable(digits=3) %>%
    kableExtra::kable_styling(full_width=FALSE) 
```

```{r}
  minDistance <- threshold.stats %>% slice_min(Dist)
  ggplot(threshold.stats, aes(x=prob_threshold, y=Dist)) +
    geom_line() +
    geom_point(data=minDistance, color="red")+
    xlab("Probability Threshold")+
    ylab("Distance to Top Left in the ROC Curve")+
    ggtitle("Distance to Top Left in the ROC Curve by Probability Threshold")
    
```



